Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\author{\IEEEauthorblockN{Alessandro Trindade}
\IEEEauthorblockA{\textit{Electricity Department} \\
\textit{Federal University of Amazonas}, Brazil \\
alessandrotrindade@ufam.edu.br}
\and
\IEEEauthorblockN{Lucas Cordeiro}
\IEEEauthorblockA{\textit{School of Computer Science} \\
\textit{University of Manchester}, UK \\
lucas.cordeiro@manchester.ac.uk }
}

@@

This paper makes the following original contributions. Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification backend for synthesizing optimal PV systems.
%
%-----------------------------------------------------------
\section{BACKGROUND}
\label{sec:AutomatedVerification}
%-----------------------------------------------------------
%
%-----------------------------------------------------------
\subsection{Program Synthesis}
\label{sec:ProgramSynthesis}
%-----------------------------------------------------------
%
The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$. In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that satisfy $\sigma$~\cite{Abateetal2017}. As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely. Counter-Example Guided Inductive Synthesis (CEGIS) represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur13}.

@@

In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs} that is incrementally updated. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates, i.e., we have found feasible equipment with the lowest cost; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again. 
%
\begin{figure}[h]
	\centering
	\includegraphics[width=0.85\columnwidth]{fig2_rev.jpg}
	\caption{Counter-Example Guided Inductive Synthesis (CEGIS) applied to PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}
%
One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.  Given that the full set of inputs $\mathcal{D}$ is finite, this means that the refinement loop can only iterate over a finite number of times; however, $\mathcal{D}$ can represent a large number of elements for the finite set $\text{\sc inputs}$ and our synthesis engine can then conclude that no feasible equipment combination was found. 
%In order to avoid exploring all possible values, machine learning techniques can be used in the phase {\sc synthesize}, with the goal of learning from experience (input-output samples), {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}. In addition to that, a pre-processing stage could also figure as another block in the scheme shown in Fig. \ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.

Nowadays, program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based automated reasoning~\cite{Sharma14}. In our particular study, we have used symbolic software verifiers based on SMT solvers to reason over QF formulas.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sizing Stand-alone Solar PV Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The sizing project check of the inverter is carried out by means of three equations. Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
%
\begin{equation}
\label{eq:vindc} 
\scriptstyle V_{in}DC = \scriptstyle V_{system}.
\end{equation}
%
\begin{equation}
\label{eq:voutac} 
\scriptstyle V_{out}AC = \scriptstyle V_{AC}.
\end{equation}
%
\begin{equation}
\label{eq:invcheck} 
\left[ (\scriptstyle Demand \leq \scriptstyle P_{AC,ref}) \, \scriptstyle and \, \scriptstyle (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}
% -------------------------------------------------------
\subsection{Optimal Sizing of PV Systems}
% -------------------------------------------------------
%
To select an optimal combination of components from a PV system, to meet sizing constraints, 
%we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
the ideal solution is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}. 
%However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC). Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
%------------------------------------------------------
\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
%------------------------------------------------------
Algorithm~\ref{alg:verification-algorithm} describes our pseudocode to synthesize stand-alone PV systems using symbolic model checking. 
%
 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \begin{scriptsize}

@@

Our evaluation aims to answer two research questions: \textit{RQ1} (soundness) Does our automated synthesis approach provide correct results?, and \textit{RQ2} (performance) How do the software verifiers compare to each other?
We have performed two case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}. Our synthesis algorithm was feed with data and costs of 22 equipment from 9 different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency. 
The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}. All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
The experiments were performed with a predefined timeout of $240$ minutes.
%
Only CPAchecker was able to present the optimal sizing of the two case studies: the result was produced in $50.2$ minutes and $37.2$ minutes, respectively. 
The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 28 from Algorithm~\ref{alg:verification-algorithm}. The results were tested by manual PV sizing and were sound (\textit{RQ1}). %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code. 
CBMC and ESBMC produced \textit{UNKNOWN} result (\textit{timeout} or \textit{out of memory}); this partially answers the \textit{RQ2}.
%
%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
\begin{table}
\caption{Case studies and Results: optimization of PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|}
\hline
\hline
Specification & \makecell{ \textbf{Case Study 1} \\ Demand=501W \\ Peak=501W \\ Energy=3,900Wh/day\\Battery autonomy=48h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC} & \makecell{\textbf{Case Study 2}\\ Demand=915W \\ Peak=980W \\Energy=4,880Wh/day\\Battery autonomy=6h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC}\\
\hline
\hline
Tools & \textbf{Result} & \textbf{Result}\\
\hline
\makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{UNKNOWN \\(Out of Memory)} & \makecell{UNKNOWN \\(Out of Memory)}\\
\hline
\makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{UNKNOWN \\(Timeout)} & \makecell{UNKNOWN \\(Timeout)} \\
\hline
%UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
%\hline
\makecell{CPAchecker 1.8 \\(MathSAT 5.5.3)} & \makecell{SAT (50.2 min) \\ Property violation line 209: \\NTP=1$\times$330W model (1S)\\NBT=8$\times$105Ah model (2S-4P)\\ Controller 15A/75V\\Inverter 700W, 48V \\ Total Cost=US\$ 1,902.60} & \makecell {SAT (37.2 min) \\ Property violation line 209:  \\NTP=3$\times$330W model (3S)\\NBT=2$\times$105Ah model (2S)\\ Controller 35A/145V \\ Inverter 1,500VA, 24V \\ Total Cost=US\$ 2,235.57}\\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}
%
We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: to include criteria as Net Present Cost, or Levelized Cost of Energy, in order to promote the acceptability of investment (or even to include operational and maintenance costs that were not considered here); (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization: this will validate the results and a simulation-verification comparative.
%
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{trindadeThesis_menor}{}

>>>>

\author{\IEEEauthorblockN{Alessandro Trindade}
\IEEEauthorblockA{
\textit{Federal University of Amazonas}, Brazil \\
alessandrotrindade@ufam.edu.br}
\and
\IEEEauthorblockN{Lucas Cordeiro}
\IEEEauthorblockA{
\textit{University of Manchester}, UK \\
lucas.cordeiro@manchester.ac.uk }
}

@@

Our work makes two major contributions. Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{abs-1811-09438}, and specifically their use in PV sizing is unprecedented. Here, a list of PV components (i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification backend for synthesizing optimal PV systems.
%
%-----------------------------------------------------------
\section{BACKGROUND}
\label{sec:AutomatedVerification}
%-----------------------------------------------------------
%
%-----------------------------------------------------------
\subsection{Program Synthesis}
\label{sec:ProgramSynthesis}
%-----------------------------------------------------------
%
The basic idea of program synthesis is to automatically construct a program $P$ that satisfies a correctness specification $\sigma$. In particular, program synthesis is automatically performed by engines that use a correctness specification $\sigma$, as starting point, and then incrementally produce a sequence of candidate solutions that satisfy $\sigma$~\cite{Abateetal2017}. As a result, a given candidate program $p$ is iteratively refined, in order to match $\sigma$ more closely. Counter-Example Guided Inductive Synthesis (CEGIS) represents one of the most popular approaches to program synthesis that are currently used in practice for CPS~\cite{Abateetal2017}, whose basic architecture is illustrated in Figure~\ref{Counter-Example-Guided-Inductive-Synthesis} and has close connections to algorithmic debugging using counterexamples and abstraction refinement~\cite{Alur13}.

@@

In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs} that is incrementally updated. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates, i.e., we have found feasible equipment with the lowest cost; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again. 
%
\begin{figure}[h]
	\centering
	\includegraphics[width=0.85\columnwidth]{fig2_rev.jpg}
	\caption{CEGIS applied to PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}
%
One may notice that each iteration of the CEGIS loop adds a new input to the finite set $\text{\sc inputs}$, which is then used for synthesis.  Given that the full set of inputs $\mathcal{D}$ is finite, this means that the refinement loop can only iterate over a finite number of times; however, $\mathcal{D}$ can represent a large number of elements for the finite set $\text{\sc inputs}$ and our synthesis engine can then conclude that no feasible equipment combination was found. 
%In order to avoid exploring all possible values, machine learning techniques can be used in the phase {\sc synthesize}, with the goal of learning from experience (input-output samples), {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}. In addition to that, a pre-processing stage could also figure as another block in the scheme shown in Fig. \ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.

Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14}; here we have used software verifiers based on SMT solvers.%Here we used software model checking techniques implemented by different tools: CBMC~\cite{Kroening}, CPAChecker~\cite{Beyer2011}, and ESBMC~\cite{esbmc2018}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sizing Stand-alone Solar PV Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The inverter sizing check is performed by means of three equations. Eq.~\eqref{eq:vindc} ensures that the input voltage of the controller meets the system voltage. Eq.~\eqref{eq:voutac} ensures that the output voltage of the controller meets the AC voltage of the load. Finally, Eq.~\eqref{eq:invcheck} ensures that the controller can support the total demand of the load ($Demand$) and the surge power ($P_{surge}$), where $V_{in}DC$ is the nominal input voltage and $V_{out}AC$ is the nominal output voltage of the inverter; $MAX_{AC,ref}$ is the peak power that the inverter can support.
%
\begin{equation}
\label{eq:vindc} 
\scriptstyle V_{in}DC = \scriptstyle V_{system}.
\end{equation}
%
\begin{equation}
\label{eq:voutac} 
\scriptstyle V_{out}AC = \scriptstyle V_{AC}.
\end{equation}
%
\begin{equation}
\label{eq:invcheck} 
\left[ (\scriptstyle Demand \leq \scriptstyle P_{AC,ref}) \, \scriptstyle and \, \scriptstyle (P_{surge} \leq MAX_{AC,ref}) \right].
\end{equation}
% -------------------------------------------------------
\subsection{Optimal Sizing of PV Systems}
% -------------------------------------------------------
%
To select an optimal combination of components from a PV system to meet sizing constraints, 
%we need to evaluate \textit{power reliability} and perform \textit{system cost} analysis for the recommended system. An ideal combination for any PV system 
the ideal solution is made by the best compromise between two objectives: power reliability and system cost~\cite{Alsadi2018}. 
Regarding power reliability, this work will rely on the critical period solar energy method~\cite{Pinho} as described in section~\ref{sec:sizing}. 
%the usual is to use loss of load probability (LOLP) or loss of power supply probability (LPSP). Based on the fact that here we are neither considering site characteristics nor the load changes over time, the reliability analysis will be developed only by the critical period method of PV sizing \textcolor{red}{What does it mean? Remember that we have software engineering audience}. 
%However, considering the system cost analysis, we usually find related studies done with Net Present Cost (NPC), Levelized Cost of Energy (LCOE), or Life Cycle Cost (LCC). Here, based on the fact that the deployment location is not specified, our study uses an adapted LCC analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
Considering the system cost analysis, based on the fact that the deployment location is not specified, our study uses an adapted Life Cycle Cost (LCC) analysis, where only the deployment cost is considered about the model, i.e., without the operational and maintenance costs~\cite{Alsadi2018}.
%------------------------------------------------------
\section{Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems}
%Applying Automated Verification to Optimal Sizing of Stand-alone Solar PV Systems}
%------------------------------------------------------
Algorithm~\ref{alg:verification-algorithm} describes our pseudocode to synthesize stand-alone PV systems using symbolic model checking. 
%
 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \begin{scriptsize}

@@

\textbf{Case studies and setup.} We have performed two case studies to evaluate our proposed synthesis approach as described in the first line of Table~\ref{tab1}. Our synthesis algorithm was feed with data and costs of 22 equipment from 9 different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency. 
The case studies are related to a stand-alone PV system with the specifications shown in Table~\ref{tab1}. All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
The experiments were performed with a predefined timeout of $240$ minutes.

\textbf{Objectives.} Our evaluation aims to answer two research questions: \textit{RQ1} (soundness) Does our automated synthesis approach provide correct results?, and \textit{RQ2} (performance) How do the software verifiers compare to each other?

\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing of both case studies: the result was produced in $50.2$ and $37.2$ minutes, respectively. 
The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 28 from Algorithm~\ref{alg:verification-algorithm}. The results were tested by manual PV sizing and were sound (\textit{RQ1}). %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code. 
CBMC and ESBMC produced \textit{UNKNOWN} result (\textit{timeout} or \textit{out of memory}); this partially answers the \textit{RQ2}.
%
%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
\begin{table}
\caption{Case studies and Results: optimization of PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|}
\hline
\hline
Specification & \makecell{ \textbf{Case Study 1} \\ Demand=501W \\ Peak=501W \\ Energy=3,900Wh/day\\Battery autonomy=48h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC} & \makecell{\textbf{Case Study 2}\\ Demand=915W \\ Peak=980W \\Energy=4,880Wh/day\\Battery autonomy=6h\\AC Voltage=120V\\DoD=25\%\\Vsystem=24V DC}\\
\hline
\hline
Tools & \textbf{Result} & \textbf{Result}\\
\hline
\makecell{CBMC 5.11 \\(MiniSat 2.2.1)} & \makecell{UNKNOWN \\(Out of Memory)} & \makecell{UNKNOWN \\(Out of Memory)}\\
\hline
\makecell{ESBMC 6.0.0 \\(Boolector 3.0.1)} & \makecell{UNKNOWN \\(Timeout)} & \makecell{UNKNOWN \\(Timeout)} \\
\hline
%UAutomizer 0.1.24 (Z3 4.8.3) & UNKNOWN & UNKNOWN \\
%\hline
\makecell{CPAchecker 1.8 \\(MathSAT 5.5.3)} & \makecell{SAT (50.2 min) \\ Property violation line 209: \\NTP=1$\times$330W model (1S)\\NBT=8$\times$105Ah model (2S-4P)\\ Controller 15A/75V\\Inverter 700W, 48V \\ Total Cost=US\$ 1,902.60} & \makecell {SAT (37.2 min) \\ Property violation line 209:  \\NTP=3$\times$330W model (3S)\\NBT=2$\times$105Ah model (2S)\\ Controller 35A/145V \\ Inverter 1,500VA, 24V \\ Total Cost=US\$ 2,235.57}\\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}

\textbf{Threats to validity.}  We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that can further be assessed and it will be future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis: to include criteria as Net Present Cost, or Levelized Cost of Energy, in order to promote the acceptability of investment (or even to include operational and maintenance costs that were not considered here); (3) to increase the equipment and manufactures data base: this will increase the complexity of the optimization but the result will also allow improved sizing; and (4) to compare the results of our approach with some off-the-shelf software that focuses on sizing and optimization: this will validate the results and a simulation-verification comparative.
%
% argument is your BibTeX string definitions and bibliography database(s)
\bibliography{trindadeThesis_menor}{}
